### 2019-03-18 papers.tex
Pull in Stefan's review of paper 23
papers.tex: Fix dumb quotes

\addtrack
	{}{Architecture: Faster and hotter}
\addpaper
	{Turing-complete chess}
	{Ross Dempsey, Sydney Timmerman, Karl Osterbauer, and Kat Xiang}
	{Keywords: chess, automata, mahogany, Turing machine}
	{SIGBOVIK_2019_paper_26}
	{0cm}
	{}
\addpaper
	{NaN gates and flip FLOPS}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: IEEE 754, mathematics, universal computation, gentleNaN}
	{SIGBOVIK_2019_paper_42}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/nand}}
\addpaper
	{HonestNN: an honest neural network "accelerator"}
	{Tim Linscott, Vidushi Goyal, Andrew McCrabb, and Pete Ehrett}
	{Keywords: accelerators, architecture, machine learning, ML, AI, DNN, CNN, graph processing, blockchain, cryptocurrency, 3D printing, security, crowdsourcing, computer, electronics, science, engineering, \#NovelResearch2019, \#BuzzwordsGetCites, \#BetterScience}
	{SIGBOVIK_2019_paper_8}
	{0cm}
	{\link[We can confirm that the authors were willing to part with a very nice bridge at a considerable discount.]{}}
\addpaper
	{Simultaneous microwaving architectures: An efficient scheme for multiplate heating}
	{Charles Yuan}
	{Keywords: high-energy physics, family and consumer sciences, computer architecture, dependent types, machine learning, Byzantine fault tolerance}
	{SIGBOVIK_2019_paper_22}
	{0cm}
	{}
\addpaper
	{Precise ECG platform on modern processors}
	{S.\@ Normalized Infloop and Ivybridge N.\@ Skylake}
	{Keywords: thermal systems, ambient heat modulating technologies, parallel heating, 2D computer graphics, edible content generation}
	{SIGBOVIK_2019_paper_33}
	{0cm}
	{}

@@

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addpaper
	{WICCAN: (deep) learning directly from the future}
	{Amanda Coston and Alan Mishler}
	{Keywords: deep learning, data-free, dark arts}
	{SIGBOVIK_2019_paper_12}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}

>>>>

\addtrack
	{}{Architecture: Faster and hotter}
\addpaper
	{Turing-complete chess}
	{Ross Dempsey, Sydney Timmerman, Karl Osterbauer, and Kat Xiang}
	{Keywords: chess, automata, mahogany, Turing machine}
	{SIGBOVIK_2019_paper_26}
	{0cm}
	{}
\addpaper
	{NaN gates and flip FLOPS}
	{Dr.\@ Tom Murphy VII Ph.D.}
	{Keywords: IEEE 754, mathematics, universal computation, gentleNaN}
	{SIGBOVIK_2019_paper_42}
	{0cm}
	{\link{https://sf.net/p/tom7misc/svn/HEAD/tree/trunk/nand}}
\addpaper
	{HonestNN: an honest neural network ``accelerator''}
	{Tim Linscott, Vidushi Goyal, Andrew McCrabb, and Pete Ehrett}
	{Keywords: accelerators, architecture, machine learning, ML, AI, DNN, CNN, graph processing, blockchain, cryptocurrency, 3D printing, security, crowdsourcing, computer, electronics, science, engineering, \#NovelResearch2019, \#BuzzwordsGetCites, \#BetterScience}
	{SIGBOVIK_2019_paper_8}
	{0cm}
	{\link[We can confirm that the authors were willing to part with a very nice bridge at a considerable discount.]{}}
\addpaper
	{Simultaneous microwaving architectures: An efficient scheme for multiplate heating}
	{Charles Yuan}
	{Keywords: high-energy physics, family and consumer sciences, computer architecture, dependent types, machine learning, Byzantine fault tolerance}
	{SIGBOVIK_2019_paper_22}
	{0cm}
	{}
\addpaper
	{Precise ECG platform on modern processors}
	{S.\@ Normalized Infloop and Ivybridge N.\@ Skylake}
	{Keywords: thermal systems, ambient heat modulating technologies, parallel heating, 2D computer graphics, edible content generation}
	{SIGBOVIK_2019_paper_33}
	{0cm}
	{}

@@

\addtrack
	{}{Back to the future}
\addpaper
	{Need more RAM? Just invent time travel!}
	{Robert Andrews, Mitchell Jones, Patrick Lin, and the UIUC Theory CS Group}
	{Keywords: complexity, Turing machine, time travel}
	{SIGBOVIK_2019_paper_23}
	{0cm}
	{}
\addreview{SIGBOVIK_2019_review_23}{0cm}
\addpaper
	{WICCAN: (deep) learning directly from the future}
	{Amanda Coston and Alan Mishler}
	{Keywords: deep learning, data-free, dark arts}
	{SIGBOVIK_2019_paper_12}
	{0cm}
	{}
\addpaper
	{On CLI-based Renderers: In which we investigate the utility of rendering teapots in a command line}
	{Michael Sandler}
	{Keywords: teapot, render, speed and performance, command-line interface, CLI, graphics}
	{SIGBOVIK_2019_paper_40}
	{0cm}
	{}
\addpaper
	{SpaceF}
	{Oscar Hernandez and The Space Invaders}
	{Keywords: space, invasion, moonshot, government, \#yeswecandotherightthingandnotgotospace, extraterrestrial intelligence, National Rifle Association, cheese, George Mallary}
	{SIGBOVIK_2019_paper_30}
	{0cm}
	{}
